Fig 2

### 2020-08-07 analysis/figure-2-new.Rmd
fig 2 margin legend foo

a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) + labs(subtitle = " ")

b <- makebargraph(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 4800, comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")

c <- makebargraph(DEGbldg, "hypothalamus", "DEGs w/ + LFC", 0, 480, comparisonlabelsbldg) +
  labs(x = "Nest-building versus all other parental stages")
d <- makebargraph(DEGchar, "hypothalamus","DEGs w/ + LFC", 0, 1700, comparisonlabelscharnobldg) +
  labs(x = "Comparison of sequential parental stages")

@@

g <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2800, comparisonlabelsbldg) 
h <- makebargraph(DEGchar, "gonad","DEGs w/ + LFC", 0, 1200, comparisonlabelscharnobldg)

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("A Hypothalamus", " " ), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1,1))
ef <- plot_grid(e,f,rel_widths = c(1,1),
                labels = c("B Pitutary"), label_size = 8 ,hjust = 0)
gh <- plot_grid(g,h,rel_widths = c(1,1), 
                labels = c("C Gonads"), label_size = 8, hjust = 0)

>>>>

b <- makebargraph(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 4800, comparisonlabelscontrol) +
  labs(subtitle = "Control versus all other reproductive and parental stages")

c <- makebargraph(DEGbldg, "hypothalamus", "DEGs w/ + LFC", 0, 480, comparisonlabelsbldg) +
  labs(subtitle = "Nest-building versus all other parental stages")
d <- makebargraph(DEGchar, "hypothalamus","DEGs w/ + LFC", 0, 1700, comparisonlabelscharnobldg) +
  labs(subtitle = "Comparison of sequential parental stages")

@@

g <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2800, comparisonlabelsbldg) 
h <- makebargraph(DEGchar, "gonad","DEGs w/ + LFC", 0, 1200, comparisonlabelscharnobldg) 
cd <- plot_grid(c,d,rel_widths = c(1,1))
ef <- plot_grid(e,f,rel_widths = c(1,1),
                labels = c("B Pitutary"), label_size = 8 ,hjust = 0)
gh <- plot_grid(g,h,rel_widths = c(1,1), 
                labels = c("C Gonads"), label_size = 8, hjust = 0)

a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) + labs(subtitle = " ")
ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("A Hypothalamus"), label_size = 8, hjust = 0)
